Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-25 NEUROC/sec3-experiment-design.tex
update
更新Reviewer2

We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{yang2016_revisiting_semisupervised, zeng2020_graphsaint, shchur2018_pitfall_of_gnn}.
%
For directed graphs, PyG converts them into undirected ones during data loading.
%
Thus, the average degree of a directed graph $\bar{d}=\frac{2|\mathcal{E}|}{|\mathcal{V}|}$.
%
For an undirected graph, the average degree is defined as $\bar{d}=\frac{|\mathcal{E}|}{|\mathcal{V}|}$.
%
For the \texttt{cam} dataset, we generated random dense feature vectors for it.
%
Since its vertices were not associated with feature vectors, we excluded it from accuracy evaluation.
%
We also used random graphs generated by the R-MAT graph generator \cite{rmat-generator} in some experiments, to explore the effects of graph topological characteristics (like average degrees) on performance bottlenecks.
%
Input feature vectors of random graphs were random dense vectors with the dimension of 32.
%
Vertices of random graphs were classified into 10 classes randomly.
%
For \texttt{amp}, \texttt{amc}, \texttt{cph}, and \texttt{cam}, we used 70\%/15\%/15\% of the samples as the training/evaluation/test set, respectively.
%
For \texttt{pub}, we used 500/1000 vertices as the evaluation/test set and the remained as the training set according to \cite{chen2018_fastgcn}.
%
For \texttt{fli}, we used 50\%/25\%/25\% of the samples as the training/evaluation/test set according to \cite{zeng2020_graphsaint}.

@@

We used Adam \cite{diederik2015_adam} as the gradient descent optimizer with a learning rate of 0.01 and a weight decay of 1e-5.
%
We initialized weights in GNNs using the method described in \cite{xavier2010_glorot} and initialized bias as zeros.
%
Without otherwise mentioned, in the experiments related to accuracy evaluation, we trained all GNNs for a maximum of 100k epochs and used the early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}:
%
the training was stopped if the validation loss did not improve for 50 epochs.
%
We chose the model parameters that achieved the lowest validation loss as the final model parameters.
%
The accuracy on the test set was evaluated with the final model.

>>>>

We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{yang2016_revisiting_semisupervised, zeng2020_graphsaint, shchur2018_pitfall_of_gnn}.
%
For directed graphs, PyG converts them into undirected ones during data loading.
%
Thus, the average degree of a directed graph $\bar{d}=\frac{2|\mathcal{E}|}{|\mathcal{V}|}$.
%
For an undirected graph, the average degree is defined as $\bar{d}=\frac{|\mathcal{E}|}{|\mathcal{V}|}$.
%
For the \texttt{cam} dataset, its vertices were not associated with feature vectors.
%
Thus, we generated random dense feature vectors for it and excluded it from accuracy evaluation.
%
For \texttt{amp}, \texttt{amc}, \texttt{cph}, and \texttt{cam}, we used 70\%/15\%/15\% of the samples as the training/evaluation/test set, respectively.
%
For \texttt{pub}, we used 500/1000 vertices as the evaluation/test set and the remained as the training set according to \cite{chen2018_fastgcn}.
%
For \texttt{fli}, we used 50\%/25\%/25\% of the samples as the training/evaluation/test set according to \cite{zeng2020_graphsaint}.
%
We also used random graphs generated by the R-MAT graph generator \cite{rmat-generator} in some experiments, to explore the effects of graph topological characteristics (like average degrees) on performance bottlenecks.
%
Input feature vectors of random graphs were random dense vectors with the dimension of 32.
%
Vertices of random graphs were classified into 10 classes randomly.

@@

We used Adam \cite{diederik2015_adam} as the gradient descent optimizer with a learning rate of 0.01 and a weight decay of 1e-5.
%
We initialized weights in GNNs using the method described in \cite{xavier2010_glorot} and initialized bias as zeros.
%
Without otherwise mentioned, in the experiments related to accuracy evaluation, we trained all GNNs for a maximum of 100k epochs and used the early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}:
%
the training was stopped if the validation loss did not improve for 50 epochs.
%
We chose the model parameters that achieved the lowest validation loss as the final model parameters.
%
The accuracy of the test set was evaluated with the final model.
